Untargeted Metabolomics

### 2021-07-13 analysis/metabolomics-targeted.Rmd
start untargeted metabolomics analysis

---
title: "Metabolomics"
subtitle: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  bookdown::pdf_document2:
    number_sections: true
    toc: true
    toc_depth: 1
    df_print: kable
    dev: cairo_pdf
    latex_engine: xelatex
geometry: margin = 0.5in
fontsize: 11pt
mainfont: Calibri
---

>>>>

---
title: "Targeted Metabolomics"
subtitle: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  bookdown::pdf_document2:
    number_sections: true
    toc: true
    toc_depth: 1
    df_print: kable
    dev: cairo_pdf
    latex_engine: xelatex
geometry: margin = 0.5in
fontsize: 11pt
mainfont: Calibri
---

### 2021-07-13 analysis/metabolomics-untargeted.Rmd
start untargeted metabolomics analysis

---
title: "Targeted Metabolomics"
subtitle: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  bookdown::pdf_document2:
    number_sections: true
    toc: true
    toc_depth: 1
    df_print: kable
    dev: cairo_pdf
    latex_engine: xelatex
geometry: margin = 0.5in
fontsize: 11pt
mainfont: Calibri
---

@@

```{r}
withr::with_dir(here::here(), {
  raw <- tar_read(metab_targeted_raw)
  clean <- tar_read(metab_targeted_clean)
  metab_pca <- tar_read(metab_targeted_pca)
  metab_limma <- tar_read(metab_targeted_limma)
  tt <- tar_read(metab_different_differences)
  volcano <- tar_read(metab_volcano)
  msea <- tar_read(msea_plot)
  leading_edge <- tar_read(leading_edge)
})
```

@@

# Data Processing

## PCA

```{r}
pcaMethods::pca(t(SummarizedExperiment::assay(raw)), scale = "uv", center = TRUE) %>% 
  pcaMethods::scores() %>% 
  merge(SummarizedExperiment::colData(raw), by = 0) %>% 
  # filter(type %nin% c("qc", "blank")) %>% 
  ggplot() +
  aes(
    x = PC1, 
    y = PC2, 
    shape = type,
    color = interaction(oxygen, treatment, sep = "|")
  ) + 
  geom_point() +
  labs(
    color = "Group", 
    shape = "Type"
  )
```
## Cleaning

1. drift correction
1. remove low quality features (QC RSD > 0.2, dispersion ratio > 0.4)
1. impute missing values with random forest
1. probabilistic quotient normalization
1. batch correction

```{r}
metab_pca
```

## Differentially regulated metabolites

```{r}
volcano
```

## Metabolite set enrichment

```{r}
msea
```

```{r}
leading_edge
```

>>>>

---
title: "Untargeted Metabolomics"
subtitle: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  bookdown::pdf_document2:
    number_sections: true
    toc: true
    toc_depth: 1
    df_print: kable
    dev: cairo_pdf
    latex_engine: xelatex
geometry: margin = 0.5in
fontsize: 11pt
mainfont: Calibri
---

@@

```{r}
withr::with_dir(here::here(), {
  pos_chrom <- tar_read(chromatograms_pos)
  neg_chrom <- tar_read(chromatograms_neg)
  pos_int <- tar_read(intensities_pos)
  neg_int <- tar_read(intensities_neg)
})
```

@@

# Data

## Preprocessing

The raw total ion intensity chromatogram were reviewed for an overview of signal acquisition quality:

```{r}
pos_chrom
neg_chrom
```

```{r}
pos_int
neg_int
```
